graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-07-04 paper/paper.Rmd
update computational details https://github.com/openjournals/joss-reviews/issues/2161

The results in this paper were obtained using R 4.0.2 with the \texttt{igraph} 1.2.5
\texttt{Matrix} 1.2-17,
\texttt{matrixcalc} 1.0-3, and \texttt{mvtnorm} 1.1-1 packages.
R itself and all dependent packages
used are available from the Comprehensive Archive Network (CRAN) at
\url{https://CRAN.R-project.org}. The \texttt{graphsim} 1.0.0 package
presented can be installed from CRAN and the issues can  be reported to
the development version on GitHub (\url{https://github.com/TomKellyGenetics/graphsim}).
This package is included in the \texttt{igraph.extensions} library on GitHub (\url{https://github.com/TomKellyGenetics/igraph.extensions})
which installs various
tools for \texttt{igraph} analysis. This software is cross-platform and
compatible with installations on Windows, Mac, and Linux operating
systems. The package GitHub repository also contains vignettes with more
information and examples on running functions released in the package.
Updates to the  package (\texttt{graphsim} 1.0.0) will be released on CRAN.

Complete examples of code needed to produce the figures in this paper are
available in the Rmarkdown version in the package GitHub repository
 (\url{https://github.com/TomKellyGenetics/graphsim/paper}).
 Further details are available in the vignettes as well.

>>>>

Complete examples of code needed to produce the figures in this paper are
available in the Rmarkdown version in the package GitHub repository
 (\url{https://github.com/TomKellyGenetics/graphsim}).
 Further details are available in the vignettes as well.

The results in this paper were obtained using R 4.0.2 with the \texttt{igraph} 1.2.5
\texttt{Matrix} 1.2-17,
\texttt{matrixcalc} 1.0-3, and \texttt{mvtnorm} 1.1-1 packages.
R itself and all dependent packages
used are available from the Comprehensive Archive Network (CRAN) at
\url{https://CRAN.R-project.org}. The \texttt{graphsim} 1.0.0 package
can be installed from CRAN and the issues can  be reported to
the development version on GitHub.
This package is included in the \texttt{igraph.extensions} library on GitHub (\url{https://github.com/TomKellyGenetics/igraph.extensions})
which installs various
tools for \texttt{igraph} analysis. This software is cross-platform and
compatible with installations on Windows, Mac, and Linux operating
systems. 
Updates to the  package (\texttt{graphsim} 1.0.0) will be released on CRAN.
